The Astropy Project

### 2017-12-12 main.tex
more info in caption

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
we show an RGB color image of the Hickson 88 group, centered near NGC~6977.
This image was generated from SDSS images using the
\package{astropy.visualization} tools.

\begin{figure}
\includegraphics[width=\textwidth]{ngc6977.png}
\caption{An RGB color image of the region near the Hickson 88 group
constructed from SDSS images and the \package{astropy.visualization}
tools.
\label{fig:ngc6977}}
\end{figure}

>>>>

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
we show an RGB color image of the Hickson 88 group, centered near
NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}}
This image was generated from SDSS images using the
\package{astropy.visualization} tools.

\begin{figure}
\includegraphics[width=\textwidth]{ngc6977.png}
\caption{An RGB color image of the region near the Hickson 88 group
constructed from SDSS images and the \package{astropy.visualization}
tools.
This example uses \package{astropy.visualization.wcsaxes} to display the
sky coordinate grid, and the \texttt{astropy.visualization.make\_lupton\_rgb()}
function to produce the RGB image from three SDSS filter images ($g$, $r$, $i$).
The left and right panel images show two different parameter choices for the
stretch and softening parameters (shown in the titles).
\label{fig:ngc6977}}
\end{figure}
